---
title: "DDSHW5"
author: "Julius Horvath"
date: "September 25, 2018"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Question 1
a. Importing the txt file and assigning to a dataframe with three columns
```{r q1a}
df<-read.delim(file = "yob2016.txt", header=FALSE, sep = ";")
names(df)<-c("FirstName", "Gender","AmountofChildren")

```
b. Display the summary and structure of df
```{r q1b}
str(df)
head(df)
summary(df)
```
c. Find the misspelled name with three y's at the end.
```{r q1c}
misspelled<-df$FirstName[grep(x=df$FirstName, pattern = ".y{3}$")]  
misspelled #I find the incorrect name is Fionayyy
```
d. Remove the name and save remained as y2016
```{r q1d}
y2016<-df[-212]
```

# Question 2
a. Import the txt file. assign to y2015
```{r q2a}
y2015<-read.csv(file="yob2015.txt", header=FALSE)
names(y2015)<-c("FirstName", "Gender","AmountofChildren")
```
b. Display the last ten rows. Describe something interesting
answer - I find it amazing that all the names are male, have the same count of five, and all begin with Z.  
```{r q2b}
tail(y2015, 10)
```
c and d. Merge y2016 and y2015 by Name, assign to final.
I created the merged dataframe, then drop the separate counts from 2015 and 2016
```{r q2c}
final<-merge(x=y2015, y=y2016, by=c("FirstName", "Gender"))
final$Total<-(final$AmountofChildren.x)+(final$AmountofChildren.y)  #creating a total column 
final$AmountofChildren.y<-NULL     #dropping the extra columns
final$AmountofChildren.x<-NULL
sortednames<-final[order(final$Total, decreasing=TRUE),]
head(sortednames$FirstName, 10)
sortedfemalenames <- final[which(final$Gender=='F'),]
sortedfemalenames<-sortedfemalenames[order(sortedfemalenames$Total, decreasing=TRUE),]
head(sortedfemalenames$FirstName, 10)
write.csv(x=c("sortedfemalenames$FirstName","sortedfemailnames$Total"), file="top10names.txt")
```